SI

### 2021-01-04 ms/si.Rmd
Fix sporo LiCl plot for 2013, 2014
Remove MgNO3 and NaCl plots for now, still need to fix

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = TRUE)
# if running interactively, source _targets.R first
# source("_targets.R")
```

@@

```{r load-functions}
# Define functions specific to this file
plot_chamber_rh <- function (data, time_limits) {
  ggplot(data, aes(x = date_time, y = 0.01*rh)) +
    geom_line() +
    scale_x_datetime(limits = time_limits) +
    scale_y_continuous(label = scales::label_percent(accuracy = 1)) +
    labs(y = "Relative humidity") +
    theme(
      legend.position = "none",
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank())
}

plot_chamber_temp <- function (data, time_limits) {
  ggplot(data, aes(x = date_time, y = temp)) +
    geom_line() +
    scale_x_datetime(limits = time_limits) +
    scale_y_continuous(label = scales::label_number(suffix = "\u00b0C", accuracy = 1)) +
    labs(y = "Temperature") +
    theme(
      legend.position = "none",
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank())
}

plot_sporo_chamber_time <- function (data, time_limits) {
    ggplot(data, aes(x = species, ymin = pre, ymax = post, y = post, group = species_duration)) +
    geom_linerange(position = position_dodge(0.5)) +
    geom_point(position = position_dodge(0.5)) +
    scale_y_datetime(limits = time_limits) +
    coord_flip() +
    labs(x = "Species") +
    theme(
      axis.title.x = element_blank()
    )
}

@@

```{r sporophyte-dt-2013-LiCl, fig.cap = ""}

# Get mean times of each cluster of DT test samples for the selected drying salt
sporo_clusters_2013 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2013")), "LiCl", 3)
sporo_clusters_2014 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2014")), "LiCl", 1)

@@

# Subset DT chamber data
licl_chamber_data_2013 <-
  filter(filmy_dt_chamber, 
         date_time >= sporo_time_range_2013[["min"]], date_time <= sporo_time_range_2013[["max"]], salt == "LiCl")
licl_chamber_data_2014 <-filter(
  filmy_dt_chamber, 
  date_time >= sporo_time_range_2014[["min"]], date_time <= sporo_time_range_2014[["max"]], salt == "LiCl")

# RH plot
rh_plot_2013 <- plot_chamber_rh(licl_chamber_data_2013, sporo_time_range_2013)
rh_plot_2014 <- plot_chamber_rh(licl_chamber_data_2014, sporo_time_range_2014)

# Temp plot
temp_plot_2013 <- plot_chamber_temp(licl_chamber_data_2013, sporo_time_range_2013)
temp_plot_2014 <- plot_chamber_temp(licl_chamber_data_2014, sporo_time_range_2014)

# Dry times plot
time_plot_2013 <- plot_sporo_chamber_time(sporo_clusters, sporo_time_range_2013)
time_plot_2014 <- plot_sporo_chamber_time(sporo_clusters, sporo_time_range_2014)

@@

**Figure S2**.

```{r sporophyte-dt-2013-MgNO3, fig.cap = ""}
plot_sporo_chamber(
  sporo_times_data = sporo_times %>% filter(species != "Callistopteris_apiifolia"), 
  filmy_dt_chamber_data = filter(filmy_dt_chamber, generation == "sporophyte"),
  salt_select = "MgNO3", 
  k_select = 3)

ggsave(here::here("results/S3_fig.pdf"))
```

**Figure S3**.

```{r sporophyte-dt-2013-NaCl, fig.cap = ""}
# Sporo NaCl plot: this includes three dataloggers with different SNs (and therefore chambers),
# but some data are missing
nacl_clusters_other <- cluster_sporo_times(
  filter(sporo_times, species != "Abrodictyum_dentatum"), 
  "NaCl", 4)

nacl_clusters_adent <- cluster_sporo_times(
  filter(sporo_times, species == "Abrodictyum_dentatum"), 
  "NaCl", 1)

nacl_clusters <- bind_rows(nacl_clusters_other, nacl_clusters_adent) %>%
  mutate(
  serial_no = case_when(
    species %in% c("Didymoglossum_tahitense", "Crepidomanes_kurzii", "Callistopteris_apiifolia") & dry_time == "2" ~ "10342561",
    species %in% c("Hymenophyllum_multifidum", "Hymenophyllum_digitatum") ~ "10140667",
    species %in% c("Hymenophyllum_polyanthos") ~ "10152774",
    species %in% c("Abrodictyum_dentatum") & dry_time == "2" ~ "missing",
    TRUE ~ "missing"
  )
)

nacl_time_range <- c(min = min(nacl_clusters$pre), max = max(nacl_clusters$post))

serial_no_cols <- brewer_pal(palette = "Dark2")(4)

# Time plot
nacl_time_plot <- ggplot(nacl_clusters, aes(x = species, ymin = pre, ymax = post, y = post, group = species_duration, color = serial_no)) +
  geom_linerange(position = position_dodge(0.5)) +
  geom_point(position = position_dodge(0.5)) +
  scale_y_datetime(limits = nacl_time_range) +
  scale_color_manual(values = c(
    "10342561" = serial_no_cols[[1]],
    "10140667" = serial_no_cols[[2]],
    "10152774" = serial_no_cols[[3]],
    "10342616" = serial_no_cols[[4]],
    "missing" = "grey20"
    )) +
  coord_flip() +
  labs(x = "Species") +
  theme(
    axis.title.x = element_blank(),
    legend.position = "none"
  )

# Subset DT chamber data
nacl_chamber_sporo_data <-
  filmy_dt_chamber %>% 
  filter(
    salt == "NaCl", 
    date_time >= nacl_time_range[["min"]], date_time <= nacl_time_range[["max"]])

# RH plot
nacl_rh_plot <- ggplot(nacl_chamber_sporo_data, aes(x = date_time, y = 0.01*rh, color = serial_no)) +
  scale_color_manual(values = c(
    "10342561" = serial_no_cols[[1]],
    "10140667" = serial_no_cols[[2]],
    "10152774" = serial_no_cols[[3]],
    "10342616" = serial_no_cols[[4]],
    "missing" = "grey20"
  )) +
  geom_line() +
  scale_x_datetime(limits = nacl_time_range) +
  scale_y_continuous(label = scales::label_percent(accuracy = 1)) +
  labs(
    y = "Relative humidity",
    color = "Data logger\nserial no.") +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank())

nacl_temp_plot <- ggplot(nacl_chamber_sporo_data, aes(x = date_time, y = temp, color = serial_no)) +
  geom_line() +
  scale_color_manual(values = c(
    "10342561" = serial_no_cols[[1]],
    "10140667" = serial_no_cols[[2]],
    "10152774" = serial_no_cols[[3]],
    "10342616" = serial_no_cols[[4]],
    "missing" = "grey20"
  )) +
  scale_x_datetime(limits = nacl_time_range) +
  scale_y_continuous(label = scales::label_number(suffix = "\u00b0C", accuracy = 1)) +
  labs(y = "Temperature") +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank())

nacl_temp_plot + nacl_rh_plot + nacl_time_plot + plot_layout(ncol = 1)

ggsave(here::here("results/S4_fig.pdf"))
```

**Figure S4**.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, results = "hide", cache = FALSE)
# if running interactively, source _targets.R first
# source("_targets.R")
```

@@

```{r load-functions}
# Define functions specific to this file
plot_chamber_rh <- function (data, time_limits) {
  ggplot(data, aes(x = date_time, y = 0.01*rh)) +
    geom_line() +
    scale_x_datetime(limits = time_limits) +
    scale_y_continuous(label = label_percent(accuracy = 1)) +
    labs(y = "Relative humidity") +
    theme(
      legend.position = "none",
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank())
}

plot_chamber_temp <- function (data, time_limits) {
  ggplot(data, aes(x = date_time, y = temp)) +
    geom_line() +
    scale_x_datetime(limits = time_limits) +
    scale_y_continuous(label = label_number(suffix = "\u00b0C", accuracy = 1)) +
    labs(y = "Temperature") +
    theme(
      legend.position = "none",
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank())
}

plot_sporo_chamber_time <- function (data, time_limits) {
    ggplot(data, aes(x = species, ymin = pre, ymax = post, y = post, group = species_duration, linetype = dry_time)) +
    geom_linerange(position = position_dodge(0.5)) +
    geom_point(position = position_dodge(0.5)) +
    scale_y_datetime(limits = time_limits) +
    scale_linetype_manual(values = c("15" = "solid", "2" = "solid")) +
    coord_flip() +
    labs(x = "Species") +
    theme(
      axis.title.x = element_blank(),
      legend.position = "none"
    )
}

@@

```{r sporophyte-dt-2013-LiCl, fig.cap = ""}
# Get mean times of each cluster of DT test samples for the selected drying salt
sporo_clusters_2013 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2013")), "LiCl", 3)
sporo_clusters_2014 <- cluster_sporo_times(filter(sporo_times, str_detect(dataset, "2014")), "LiCl", 1)

@@

# Subset DT chamber data
licl_chamber_data_2013 <-
  filter(filmy_dt_chamber, 
    date_time >= sporo_time_range_2013[["min"]], 
    date_time <= sporo_time_range_2013[["max"]], 
    salt == "LiCl")
licl_chamber_data_2014 <- 
  filter(filmy_dt_chamber, 
    date_time >= sporo_time_range_2014[["min"]], 
    date_time <= sporo_time_range_2014[["max"]], 
    salt == "LiCl") %>%
  # There are two sets of times: 2014-06-17 to 2014-07-02, and 2014-07-06 to 2014-07-08
  # Add a group for these so ggplot doesn't connect lines betweeen them
  mutate(
    day = yday(date_time),
    group = ifelse(day < 185, "a", "b"))

licl_chamber_data <- bind_rows(licl_chamber_data_2013, licl_chamber_data_2014)
licl_temp_range <- c(min(licl_chamber_data$temp), max(licl_chamber_data$temp))
licl_rh_range <- c(min(licl_chamber_data$rh), max(licl_chamber_data$rh))*0.01

# RH plot
rh_plot_2013 <- plot_chamber_rh(licl_chamber_data_2013, sporo_time_range_2013) +
  scale_y_continuous(limits = licl_rh_range, label = label_percent(accuracy = 1))

rh_plot_2014 <- ggplot(licl_chamber_data_2014, aes(x = date_time, y = 0.01*rh, group = group)) +
  geom_line() +
  scale_x_datetime(limits = sporo_time_range_2014) +
  blank_x_theme() +
  blank_y_theme() +
  theme(legend.position = "none")

# Temp plot
temp_plot_2013 <- plot_chamber_temp(licl_chamber_data_2013, sporo_time_range_2013) +
  scale_y_continuous(limits = licl_temp_range, label = label_number(suffix = "\u00b0C", accuracy = 1))

temp_plot_2014 <- ggplot(licl_chamber_data_2014, aes(x = date_time, y = temp, group = group)) +
  geom_line() +
  scale_x_datetime(limits = sporo_time_range_2014) +
  blank_x_theme() +
  blank_y_theme() +
  theme(legend.position = "none")

# Dry times plot
time_plot_2013 <- plot_sporo_chamber_time(sporo_clusters, sporo_time_range_2013) +
  labs(y = "2013") +
  theme(axis.title.x = element_text()) 
time_plot_2014 <- plot_sporo_chamber_time(sporo_clusters, sporo_time_range_2014)  +
  labs(y = "2014")  +
  theme(axis.title.x = element_text()) +
  blank_y_theme()

@@

**Figure S2**. Conditions inside desiccation chamber and duration of desiccation treatment for sporophytes at most intense desiccation level. LiCl was used to maintain constant humidity at \circa{ }18%.
